---
title: Swirl
weight: 3
slug: swirl
---

The `swirl` package for _R_ was developed by the Swirl Development Team, and includes a suite of step-by-step interactive training courses on _R_, which are aimed primarily at the novice and intermediate user. Before starting this course you should at the very least be familiar with the content of the `swirl` course: **'R Programming'**. During the course, we shall also complete all or parts of the `swirl` courses: **'Getting and Cleaning Data'**, and **'Exploratory Data Analysis'**. You can look at the full suite of `swirl` courses that are available [here](https://github.com/swirldev/swirl_courses#swirl-courses){ target="_blank" }.

Follow the instructions below to install and load the `swirl` package:

```{r eval = FALSE}
# Re-type or copy and paste the text below into the R console, 
# pressing 'Enter' after each step.

# If you haven't already installed swirl
install.packages('swirl')

# Once the package is installed, load the 'swirl' package
library(swirl)

# Launch a 'swirl' session and follow the prompts
swirl()
```

...and to install `swirl` courses:

```{r eval = FALSE}
# Re-type or copy and paste the text below into the R console, 
# pressing 'Enter' after each step.

# Load the 'swirl' package
library(swirl)

# Download a course from the 'swirl' github repository
## Course names:
### 'R Programming Alt'
### 'Getting and Cleaning Data'
### 'Exploratory Data Analysis'
install_from_swirl('Course Name Here')

# Launch a 'swirl' session and follow the prompts
swirl()
```
